### 2020-09-23 Analysis/Code/Paper.Rmd
Added the tests on average like probabilities.

# Empirical Model of Demand

\textcolor{red}{Write a small introduction here.}

@@

The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion. Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the positive treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(re23$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount. Proximity to a potential negative transition seems to have negative or no effect on the probability of discount. The results in the main specification suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))` less likely to go on a discount, albeit the effect is not significant in the other two specifications.

@@

It is instructive to look at the results through the lens of stylized model introduced earlier in the section. Take the products close to a review upgrade first. For such products to choose to not go on a discount, the downside risk of doing so should be high, or they must have enough reviews to make changing their review score infeasible. Both scenarios would appear to be relatively unrealistic ex ante, and my results for firms on the verge of a positive transition comply with that expectation. On the other hand, the predictions for games that are close to a review downgrade were more blurred. It is reasonable to expect such products to dislike variance, unless the upside risk is strong. That would be the case reviews left during a discount are more positive, or if better review labels increase sales by a lot.

The results I presented in this section, therefore, lead to the following hypothesis: reviews left on a discount are not more positive than the ones left off a discount. If this hypothesis is not true, the lack of discounting by products close to a negative transition would be puzzling. This hypothesis has found some support in the prior literature, albeit in a different market. @ByersEtAl12 and @Li16 report that customers who choose to go to a restaurant because of a price promotion tend to leave worse reviews, even though the effect could be positive in certain cases [@Li16; @ZhuEtAl19]. Theoretically, this effect of buying on a discount on the valence of the review ambiguous. Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews. At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leave better reviews [@CabralLi15; @IfrachEtAl19; @AcemogluEtAl19]. I now turn my attention to investigating this hypothesis, as doing so would be helpful in assessing the results obtained in this section, and would contribute to the literature by providing evidence from a new market.

# Selection Effect of Discounts

@@

\begin{assumption}\label{likeDiscountAss}
The like rate is a linear function of discounts:
$r_{it}^+ = \rho_{0i}^+ + \rho_{1i}^+ disc_{it-k}$.  The dislike rate is a linear function of discounts: $r_{it}^- = \rho_{0i}^- + \rho_{1i}^- disc_{it-k}$.
\end{assumption}

\noindent Notice, that a price change affects the reviewing behavior in two ways. First, a lower prices increases the inflow of buyers through a higher $\lambda_{it}$. This leads to more reviews being left. My parametrization allows to further study if the reviewers who bought the game on a discount are more or less likely to leave positive and negative reviews. I use a dummy variable $disc_{it-k}$ to measure discounting because this will allow me to derive a closed-form estimator for the  parameters of interest.

@@

```{r}
panel[, disc:=c(shift((discount > 0))), by = ID]
panel[, lam:=shift(lambda), by = ID]
panel[is.na(pReviews), pReviews := 0]
panel[is.na(nReviews), nReviews := 0]

revs <- panel[!(is.na(lam)), .(t, disc, lam, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]

revs.lik <- function(x){
  revs[, r.plus := x[1] + disc*x[2], by = ID]
  revs[, r.minus := x[3] + disc*x[4], by = ID]

  return(list(
    "objective" = -revs[, sum(l * log(r.plus) - r.plus*lam +  
                             d * log(r.minus) - r.minus*lam)],
    "gradient" = -c(revs[, sum(l/r.plus - lam)],
                   revs[, sum((l/r.plus - lam)*disc)],
                   revs[, sum(d/r.minus - lam)],
                   revs[, sum((d/r.minus - lam)*disc)])
  ))
}

library(nloptr)

x0 <- c(0.25, 0.0, 0.05, 0.0)
max.lik <- nloptr(x0, 
                  revs.lik,
                  lb = c(0, -1, 0, -1),
                  ub = c(10, 2, 10, 2),
                  opts = list(algorithm = "NLOPT_LD_LBFGS"))

x <- max.lik$solution
```

@@

```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$'}
p1 <- ggplot(data = revs[, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 alpha = 0.9,
                 binwidth = 0.1,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Change in Like Rates",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     breaks = c(0, 1, 2),
                     minor_breaks = NULL) +
  my.theme() +
  coord_cartesian(xlim = c(-0.5, 2))

p2 <- ggplot(data = revs[, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 binwidth = 0.025,
                 alpha = 0.9,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Change in Dislike Rates",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     minor_breaks = NULL) +
  my.theme() +
  coord_cartesian(xlim = c(-0.5, 2))

```{r like-rates, fig.width = 8, fig.height = 6, include = FALSE}
ggarrange(p1, p2, nrow=2, align = "v")
```

The main parameters of interest in this section are $(\rho_{1i}^+, \rho_{1i}^-)$, which measure the change in the like and dislike rates during discounts. The precision with which this parameter could be estimated for game $i$ depends on the number of discount days we observe for that game. For some products it is impossible to estimate the parameter precisely, either due to their short presence in the sample, insufficient number of discounts, or both. However, out of `r info[, .N]` games in the sample, `r revs[posSignif == T, .N]` have a value of $\rho_{1i}^+$ that is statistically different from zero, and `r revs[negSignif == T, .N]` have a value of $\rho_{1i}^-$ that is statistically different from zero. The distributions of $\rho_{1i}^+$ and $\rho_{1i}^-$ all games (excluding some outliers) are plotted in Figure \ref{likeRatesPlot}. These plots reveal two patterns. The first is that there are a lot of products whose consumers leave positive and/or negative feedback with the same probability on and off a discount, as is reflected in high density of the histograms close to zero. Second, the like rates appear to be way more responsive to discounts than the dislike rates.

These findings require some interpretation. @Li16 claims “It is by now almost accepted as a stylized fact that offering deal promotion [...] deteriorates local merchants' online reputations”, while my findings seem to suggest that discounts improve review scores. Column (2) in Table \ref{reviewLag} in the Appendix presents the results of 
regressing review score on days after a discount (with controls). The results suggest that, on average, the review score goes down, not up, in the days following a discount. The total effect at best adds up to 1 point out of a 100, but, technically, my findings do not contradict the literature. Instead, I show that there is a long tail of products that receive significantly better reviews during a price promotion. The main hypothesis that I am developing in this paper is that firms use discounting to manage their online reputation. This hypothesis implies that firms that  receive better reviews during price promotions should be more likely to engage in such behavior. Thus, my goal in this section is not to study the heterogeneity in the response of the review sentiment to discounts for its own sake, but simply to identify games that my hypothesis predicts should exhibit stronger effects. However, my findings present an interesting puzzle for future investigation: how does the (average) negative response of review score to discounts coexist with the distribution of products that seem to receive better reviews during discounts, not worse.

\textcolor{red}{Looks like consumers are more likely to leave reviews during a discount. That could be interesting. Calculate standard errors for that?}

## Revisiting Discounting and Transitions

Now that I have estimated the parameters of the demand and review processes, I am ready to use them to revisit my
main hypothesis. In Section \ref{descriptiveEvidence} I have established that

```{r results = 'asis', warning = FALSE}
# remove 1% with the highest values of rho_1+ (<=2)
# and only keep significant coefficients
panel <- merge(panel, revs[, .(ID, rho1 = rhoPosD - rhoPosND, score.dif)])

panel[, pos.treatment := (needPos <= 2*band)]
panel[, neg.treatment := (needNeg <= 2*band)]

reg1 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5,],
           model = "pooling")
cov<-vcovHC(reg1, method="white1")
se1 <- sqrt(diag(cov))

reg2 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5 & 
                        ID %in% revs[negSignif == T | posSignif == T, ID], 
                        ],
           model = "pooling")
cov<-vcovHC(reg2, method="white1")
se2 <- sqrt(diag(cov))

reg3 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5
                        # ID %in% revs[negSignif == T | posSignif == T, ID], 
                        ],
           model="within",
           index = c("ID", "t"))
cov<-vcovHC(reg3, method = "white1")
se3 <- sqrt(diag(cov))

reg4 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5 & 
                        ID %in% revs[negSignif == T | posSignif == T, ID], 
                        ],
           model="within",
           index = c("ID", "t"))
cov<-vcovHC(reg4, method = "white1")
se4 <- sqrt(diag(cov))

star.out<-stargazer(reg1, reg2, reg3, reg4,
                    label = "rhoTransDiscReg",
                    header = FALSE,
                    title = "Discounts Before Potential Transitions And Firm Heterogeneity",
                    se=list(se1, se2, se3, se4),
                    dep.var.labels = c("$\\mathbb{P}(Discount)$"),
                    column.labels=c("OLS", "OLS:Signif", "FE", "FE:Signif"),
                    model.numbers = F,
                    omit = c("tWODisc", "reviews", "noScore", "realPositive", 
                             "mPositive", "vPositive", "age", "young", "Constant",
                             "score", "day", "week", "needPosDays", "needNegDays"),
                    covariate.labels = c("$\\rho_1^+$",
                                         "$\\rho_1^+ \\times$ Pos. Tr.",
                                         "$\\rho_1^+ \\times$ Neg. Tr.",
                                         "Pos. Tr.", "Neg. Tr."),
                    order = c("rho1"),
                    omit.stat=c("f","adj.rsq","ser"),
                    no.space=T)
```

@@

reg3 <- plm(score ~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
                           discNewLag5 + discNewLag6 + discNewLag7 +
                           negative + mPositive + realPositive + vPositive + ovPositive +
                           log(reviews + 1) + age + young + day + week,
                           data = panel, model="within",             index = c("ID", "t"))
cov<-vcovHC(reg3, method="white1")
se3 <- sqrt(diag(cov))

>>>>

# Empirical Model of Demand
\label{demandSection}
\textcolor{red}{Write a small introduction here.}

@@

The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion. Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the positive treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg2$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount. Proximity to a potential negative transition seems to have negative or no effect on the probability of discount. The results in the main specification suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))` less likely to go on a discount, albeit the effect is not significant in the other two specifications.

@@

It is instructive to look at the results through the lens of stylized model introduced earlier in the section. Take the products close to a review upgrade first. For such products to choose to not go on a discount, the downside risk of doing so should be high, or they must have enough reviews to make changing their review score infeasible. Both scenarios would appear to be relatively unrealistic ex ante, and my results for firms on the verge of a positive transition comply with that expectation. On the other hand, predictions for games that are close to a review downgrade were more blurred. It is reasonable to expect such products to dislike variance, unless the upside risk is strong. The upside risk would be strong if reviews left during a discount were more positive, or if better review labels increased sales by a lot. I find no positive, nor negative effect of proximity to a negative transition on discounting behavior, which indicates that pros and cons balance out.

The results I presented in this section, therefore, lead to the following hypothesis: reviews left on a discount are not more positive than the ones left off a discount. If this hypothesis is not true, the lack of discounting by products close to a negative transition would be puzzling. This hypothesis has found some support in the prior literature, albeit in a different market. @ByersEtAl12 and @Li16 report that customers who choose to go to a restaurant because of a price promotion tend to leave worse reviews, even though the effect could be positive in certain cases [@Li16; @ZhuEtAl19]. Theoretically, this effect of buying during a discount on the valence of the reviews is ambiguous. Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews. At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leave better reviews [@CabralLi15; @IfrachEtAl19; @AcemogluEtAl19]. I now turn my attention to investigating this hypothesis, as doing so would be helpful in assessing the results obtained in this section, and would contribute to the literature by providing evidence from a new market.

# Discounts and Reviewing Behavior

In the previous section I established two key facts. First, I found that firms are more likely to go on a discount when their products are close to upgrading their review bin. Second, I did not find any change in the discounting behavior for products that are close to downgrading their review bins. My theory of disconting in the face of review transitions, applied to these findings, implies that reviews left during a discount can not be significantly better than regular reviews, as otherwise the lack of discounting by products close to a review downgrade is puzzling. But if reviews obtained during a discount are not very different from the regular reviews, it has to be the case that discounts fascilitate the arrival of reviews, providing firms with extra variance when they want to speed things up. Otherwise, discounting by firms close to a positive transition would be puzzling. In this section I investigate if these two hypotheses about the valence and quantity of reviews left during price promotions hold in data.

To formulate and test these hypotheses, I complement my model of demand and gaming on Steam introduced in Section \ref{demandSection} by a model of reviewing behavior. A formal model of reviewing behavior is necessary for several reasons. First, a structural model allows me to explicitly introduce the parameters of interest--probabilities of leaving a good or a bad reviews on and off a discount. Second, more importantly, the model will allow me to use my estimates of the demand process to make statements about the absolute change in probability of leaving a review that is due to the discount. One does not need a model to check if more reviews are left during a price promotion--a simple comparison of means would do. However, since sales are unobserved, it is impossible to say if the new reviews are entirely due to the influx of new customers, or part of it could be explained by an increased willingness to leave a review during a discount. I use my model to estimate sales, and therefore I can make inference on the propensity to leave a review. Note that most studies studying reviewing behavior do not observe anything close to daily sales, and thus could not possibly have indentified the effects I am interested here.

As a preview of results, I do find that customers are significantly more likely to review a product if they purchase it during a price promotion, albeit the valence of the reviews is unaffected, on average. In other words, I provide evidence that, in my data, the negative selection effect of lower prices on the type of customers leaving reviews that has been documented in the literature does not outweigh the direct effect of lower prices on their satisfaction and their review decision. I then proceed to allow firms in my sample to be heterogeneous in the probabilities of recieving positive and negative reviews on and off discount. I check if firms whose customers are particularly likely to leave a like during a discount are more likely to discount, and I find some support for this hypothesis.

## Review Model

@@

\begin{assumption}\label{likeDiscountAss}
The like rate is a linear function of covariates $w_{it} = [1, disc_{it}, \ldots]'$:
$r_{it}^+ = w_{it}'\rho_i^+$.  The dislike rate is a linear function of covariates: $r_{it}^- = w_{it}'\rho_i^-$.
\end{assumption}

In the simplest specification I use $w_{it} = [1, disc_{it}]'$, $\forall i: \rho_i^+ = \rho^+$,  implying $r_{it}^+ = \rho^+_0 + disc_{it}\rho^+_1$, which simply says that buyers of all games leave a positive reviews with one of two possible probabilities: $\rho^+_0$ off a discount, and $\rho^+_0 + \rho^+_1$ on a discount. Similarly, a probability of a negative review could be either $\rho^-_0$, or $\rho^-_0 + \rho^-_1$. While the model with no heterogeneity in parameters is not very realistic (for one, it implies that all games have the same expected review score), I treat the estimates that will come out of it as estimates of average parameter values: $\rho^+ \approx \bar{\rho}_i^+$, $\rho^- \approx \bar{\rho}_i^-$. Thus, a model without heterogeneiry offers a simple way to do inference on the average values of parameters in the population of games.

As I explained in the introduction, I want to know if consumers are more likely to leave a review if they buy on a discount. This amounts to testing $\rho^+_0 + \rho^+_1 + \rho^-_0 + \rho^-_1 > \rho^+_0 + \rho^-_0$, or
\begin{equation}\label{hypProbReview}
  \rho^+_1 + \rho^-_1 > 0
\end{equation}
\noindent The second hypothesis I am interested in involves the sentiment of the reviews left on and off a discount. Product's review score measures the fraction of positive reviews among all reviews left, reflecting the probability to get a good review conditional on having a review. Formally, the expected review score of a game that never discounts is
$$\EE{Score_{it}} = $$

@@

```{r}
# In this module I estimate the average like and dislike rates on and off discount,
# and I test whether: (a) users leave better reviews on a discount, (b) users leave
# more reviews during discounts
panel[, disc:=c(shift((discount > 0))), by = ID]
panel[, lam:=shift(lambda), by = ID]
panel[is.na(pReviews), pReviews := 0] # remove this, it is already in CreateSample
panel[is.na(nReviews), nReviews := 0] # remove this, it is already in CreateSample

# part of the panel that has new reviews and estimated arrivals
revs <- panel[!(is.na(lam)), .(t, lam, l = c(pReviews[1], diff(pReviews)), 
                               d = c(nReviews[1], diff(nReviews)), const = 1, 
                               zero = 0 ), by=ID]

regressors <- c("disc", "young", "age")
revs <- merge(revs, panel[!(is.na(lam)), c("ID", "t", regressors), with = F],
              by = c("ID", "t"))
revs[, old := age >= 365][, age := NULL]
# NOTE: the first two regressors have to be "const" and "disc"
regressors <- c("const", "disc", "young", "old")
k <- length(regressors)

# negative of the likelihood function
revs.lik <- function(x){

  revs[, r.plus := as.matrix(revs[, regressors, with = F]) %*% x[1:k]]
  revs[, r.minus := as.matrix(revs[, regressors, with = F]) %*% x[(k+1):(2*k)]]

  gradient.plus <- revs[, l/r.plus - lam] %*% as.matrix(revs[, regressors, with = F])
  gradient.minus <- revs[, d/r.minus - lam] %*% as.matrix(revs[, regressors, with = F])
  return(list(
    "objective" = -revs[, sum(l * log(r.plus) - r.plus*lam +  
                             d * log(r.minus) - r.minus*lam)],
    "gradient" = -rbind(t(gradient.plus), t(gradient.minus))
  ))
}

# maximize the likelihood to estimate the parameters
library(nloptr)
x0 <- c(c(0.25, rep(0, k-1)), c(0.25, rep(0, k-1)))
max.lik <- nloptr(x0, 
                  revs.lik,
                  lb = c(0, 0, 0, -0.1, 0, 0, 0, -0.1),
                  ub = rep(2, length(x0)),
                  opts = list(algorithm = "NLOPT_LD_LBFGS"))

theta <- max.lik$solution

# Estimate E[score score']
sigma.hat <- function(x){
  n <- dim(revs)[1]
  revs[, r.plus := as.matrix(revs[, regressors, with = F]) %*% x[1:k]]
  revs[, r.minus := as.matrix(revs[, regressors, with = F]) %*% x[(k+1):(2*k)]]

  ans <- matrix(rep(0, 4*k^2), nrow = (2*k))

  for (i in 1:n){
    gradient.plus <- t(revs[i, l/r.plus - lam] * as.matrix(revs[i, regressors, with = F]))
    gradient.minus <- t(revs[i, d/r.minus - lam] * as.matrix(revs[i, regressors, with = F]))
    score <- rbind(gradient.plus, gradient.minus)
    ans <- ans + score %*% t(score)
  }

  return(ans/n)
}

# Estimate the hessian d(score)/d theta'
H.hat <- function(x){
  n <- dim(revs)[1]
  revs[, r.plus := as.matrix(revs[, regressors, with = F]) %*% x[1:k]]
  revs[, r.minus := as.matrix(revs[, regressors, with = F]) %*% x[(k+1):(2*k)]]

  H <- matrix(rep(0, 4*k^2), nrow = (2*k))

  for (i in 1:n){
    zeros <- rep("zero", k)
    h1 <- revs[i, c(regressors, zeros), with = F] %>% as.matrix() %>% matrix(., nrow = 1)
    h2 <- revs[i, c(zeros, regressors), with = F] %>% as.matrix() %>% matrix(., nrow = 1)
    dr.drho <- rbind(h1, h2)
    dlik.dr <- revs[i, .(-l/((r.plus)^2), 0, 0, -d/((r.minus)^2))] %>%
               as.matrix() %>% matrix(., nrow = 2)
    H <- H + t(dr.drho) %*% dlik.dr %*% dr.drho
  }

  return(H/n)
}

# calculate the variance-covariance matrix of theta hat (asymptotic divided by n)
sigma <- sigma.hat(theta)
H <- H.hat(theta)
H.inv <- solve(H, diag(1, nrow = (2*k)))
omega <- (H.inv %*% sigma %*% H.inv) / dim(revs)[1]

# Test if the probability to leave a review goes up: 
# a(theta) = theta[2] + theta[2+k]
# Null: a(theta_0) = 0
A <- rep(0, 2*k)
A[2] <- 1
A[2+k] <- 1
# t stat
(theta[2] + theta[2+k])/sqrt(t(A) %*% omega %*% A)

# Test if the probability to leave a like conditional on review (score) goes up
# with a discount
# a(theta) = (theta[1] + theta[1+k])/(sum(theta[c(1,2,1+k,2+k)])) - theta[1]/(theta[1] + theta[1+k])
grad.a <- function(x){

  ans <- rep(0, length(x))
  sum.x <- sum(x[c(1,2,1+k,2+k)])

  ans[1] <- (sum.x - x[1]) / (sum.x)^2 - x[1+k]/(x[1] + x[1+k])^2
  ans[2] <- (sum.x - x[2]) / (sum.x)^2
  ans[1+k] <- (- x[1] - x[2]) / (sum.x)^2  + x[1]/(x[1] + x[1+k])^2
  ans[2+k] <- (- x[1] - x[2]) / (sum.x)^2

  return(ans)
}

A <- grad.a(theta)

score.dif <- (theta[1] + theta[2])/(sum(theta[c(1,2,1+k,2+k)])) - 
             (theta[1])/(theta[1] + theta[1+k])

score.dif/sqrt(t(A) %*% omega %*% A)
```

@@

<!-- ```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$'} -->
<!-- p1 <- ggplot(data = revs[, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) + -->
<!--   geom_histogram(mapping = aes(x = x, y = ..density..), -->
<!--                  color = "black", -->
<!--                  position = "identity", -->
<!--                  boundary = 0, -->
<!--                  alpha = 0.9, -->
<!--                  binwidth = 0.1, -->
<!--                  fill = my.colors[1]) + -->
<!--   geom_density(mapping = aes(x = x), -->
<!--                  color = "black", -->
<!--                  position = "identity", -->
<!--                  alpha = 0.4, -->
<!--                  fill = my.colors[1]) + -->
<!--   scale_x_continuous(name = "Change in Like Rates", -->
<!--                      minor_breaks = NULL) + -->
<!--   scale_y_continuous(name = NULL, -->
<!--                      breaks = c(0, 1, 2), -->
<!--                      minor_breaks = NULL) + -->
<!--   my.theme() + -->
<!--   coord_cartesian(xlim = c(-0.5, 2)) -->

<!-- p2 <- ggplot(data = revs[, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) + -->
<!--   geom_histogram(mapping = aes(x = x, y = ..density..), -->
<!--                  color = "black", -->
<!--                  position = "identity", -->
<!--                  boundary = 0, -->
<!--                  binwidth = 0.025, -->
<!--                  alpha = 0.9, -->
<!--                  fill = my.colors[1]) + -->
<!--   geom_density(mapping = aes(x = x), -->
<!--                  color = "black", -->
<!--                  position = "identity", -->
<!--                  alpha = 0.4, -->
<!--                  fill = my.colors[1]) + -->
<!--   scale_x_continuous(name = "Change in Dislike Rates", -->
<!--                      minor_breaks = NULL) + -->
<!--   scale_y_continuous(name = NULL, -->
<!--                      minor_breaks = NULL) + -->
<!--   my.theme() + -->
<!--   coord_cartesian(xlim = c(-0.5, 2)) -->

<!-- ggarrange(p1, p2, nrow=1, align = "h") -->
<!-- ``` -->

<!-- ```{r like-rates, fig.width = 8, fig.height = 6, include = FALSE} -->
<!-- ggarrange(p1, p2, nrow=2, align = "v") -->
<!-- ``` -->

<!-- The main parameters of interest in this section are $(\rho_{1i}^+, \rho_{1i}^-)$, which measure the change in the like and dislike rates during discounts. The precision with which this parameter could be estimated for game $i$ depends on the number of discount days we observe for that game. For some products it is impossible to estimate the parameter precisely, either due to their short presence in the sample, insufficient number of discounts, or both. However, out of `r info[, .N]` games in the sample, `r revs[posSignif == T, .N]` have a value of $\rho_{1i}^+$ that is statistically different from zero, and `r revs[negSignif == T, .N]` have a value of $\rho_{1i}^-$ that is statistically different from zero. The distributions of $\rho_{1i}^+$ and $\rho_{1i}^-$ all games (excluding some outliers) are plotted in Figure \ref{likeRatesPlot}. These plots reveal two patterns. The first is that there are a lot of products whose consumers leave positive and/or negative feedback with the same probability on and off a discount, as is reflected in high density of the histograms close to zero. Second, the like rates appear to be way more responsive to discounts than the dislike rates. -->

<!-- These findings require some interpretation. @Li16 claims “It is by now almost accepted as a stylized fact that offering deal promotion [...] deteriorates local merchants' online reputations”, while my findings seem to suggest that discounts improve review scores. Column (2) in Table \ref{reviewLag} in the Appendix presents the results of  -->
<!-- regressing review score on days after a discount (with controls). The results suggest that, on average, the review score goes down, not up, in the days following a discount. The total effect at best adds up to 1 point out of a 100, but, technically, my findings do not contradict the literature. Instead, I show that there is a long tail of products that receive significantly better reviews during a price promotion. The main hypothesis that I am developing in this paper is that firms use discounting to manage their online reputation. This hypothesis implies that firms that  receive better reviews during price promotions should be more likely to engage in such behavior. Thus, my goal in this section is not to study the heterogeneity in the response of the review sentiment to discounts for its own sake, but simply to identify games that my hypothesis predicts should exhibit stronger effects. However, my findings present an interesting puzzle for future investigation: how does the (average) negative response of review score to discounts coexist with the distribution of products that seem to receive better reviews during discounts, not worse. -->

<!-- \textcolor{red}{Looks like consumers are more likely to leave reviews during a discount. That could be interesting. Calculate standard errors for that?} -->

<!-- ## Revisiting Discounting and Transitions -->

<!-- Now that I have estimated the parameters of the demand and review processes, I am ready to use them to revisit my -->
<!-- main hypothesis. In Section \ref{descriptiveEvidence} I have established that  -->

<!-- ```{r results = 'asis', warning = FALSE} -->
<!-- # remove 1% with the highest values of rho_1+ (<=2) -->
<!-- # and only keep significant coefficients -->
<!-- panel <- merge(panel, revs[, .(ID, rho1 = rhoPosD - rhoPosND, score.dif)]) -->

<!-- panel[, pos.treatment := (needPos <= 2*band)] -->
<!-- panel[, neg.treatment := (needNeg <= 2*band)] -->

<!-- reg1 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
<!--            data = panel[rho1 <= 2 & rho1 >= -0.5,], -->
<!--            model = "pooling") -->
<!-- cov<-vcovHC(reg1, method="white1") -->
<!-- se1 <- sqrt(diag(cov)) -->

<!-- reg2 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
<!--            data = panel[rho1 <= 2 & rho1 >= -0.5 &  -->
<!--                         ID %in% revs[negSignif == T | posSignif == T, ID],  -->
<!--                         ], -->
<!--            model = "pooling") -->
<!-- cov<-vcovHC(reg2, method="white1") -->
<!-- se2 <- sqrt(diag(cov)) -->

<!-- reg3 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
<!--            data = panel[rho1 <= 2 & rho1 >= -0.5 -->
<!--                         # ID %in% revs[negSignif == T | posSignif == T, ID],  -->
<!--                         ], -->
<!--            model="within", -->
<!--            index = c("ID", "t")) -->
<!-- cov<-vcovHC(reg3, method = "white1") -->
<!-- se3 <- sqrt(diag(cov)) -->

<!-- reg4 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
<!--            data = panel[rho1 <= 2 & rho1 >= -0.5 &  -->
<!--                         ID %in% revs[negSignif == T | posSignif == T, ID],  -->
<!--                         ], -->
<!--            model="within", -->
<!--            index = c("ID", "t")) -->
<!-- cov<-vcovHC(reg4, method = "white1") -->
<!-- se4 <- sqrt(diag(cov)) -->

<!-- star.out<-stargazer(reg1, reg2, reg3, reg4, -->
<!--                     label = "rhoTransDiscReg", -->
<!--                     header = FALSE, -->
<!--                     title = "Discounts Before Potential Transitions And Firm Heterogeneity", -->
<!--                     se=list(se1, se2, se3, se4), -->
<!--                     dep.var.labels = c("$\\mathbb{P}(Discount)$"), -->
<!--                     column.labels=c("OLS", "OLS:Signif", "FE", "FE:Signif"), -->
<!--                     model.numbers = F, -->
<!--                     omit = c("tWODisc", "reviews", "noScore", "realPositive",  -->
<!--                              "mPositive", "vPositive", "age", "young", "Constant", -->
<!--                              "score", "day", "week", "needPosDays", "needNegDays"), -->
<!--                     covariate.labels = c("$\\rho_1^+$", -->
<!--                                          "$\\rho_1^+ \\times$ Pos. Tr.", -->
<!--                                          "$\\rho_1^+ \\times$ Neg. Tr.", -->
<!--                                          "Pos. Tr.", "Neg. Tr."), -->
<!--                     order = c("rho1"), -->
<!--                     omit.stat=c("f","adj.rsq","ser"), -->
<!--                     no.space=T) -->
<!-- ``` -->

@@

reg3 <- plm(score ~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
                           discNewLag5 + discNewLag6 + discNewLag7 +
                           # negative + mPositive + realPositive + vPositive + ovPositive +
                           log(reviews + 1) + age + young + day + week,
                           data = panel, model="within",             index = c("ID", "t"))
cov<-vcovHC(reg3, method="white1")
se3 <- sqrt(diag(cov))

star.out <- stargazer(reg1, reg2, reg3, 
             label = "reviewLag",
             table.placement = "hp",
             header = FALSE,
             title = "Changes in Review Flows and Score After a Discount",
             se=list(se1, se2, se3),
             dep.var.labels = c("New Reviews", "New Reviews(\\%)", "Score (0-100)"),
             covariate.labels = c("Discount 0 Days Ago", "Discount 1 Day Ago",
                                  "Discount 2 Days Ago", "Discount 3 Days Ago",
                                  "Discount 4 Days Ago", "Discount 5 Days Ago",
                                  "Discount 6 Days Ago", "Discount 7 Days Ago"),
             model.numbers = F,
             omit = c("day","week","negative","mPositive","realPositive",
                      "vPositive", "ovPositive", "reviews", "score", "age", "young"),
             omit.stat=c("f","adj.rsq","ser"),
             no.space=T)
panel[, discNewLag2:=NULL][, discNewLag3:=NULL][, discNewLag4:=NULL][, discNewLag5:=NULL]
panel[, discNewLag6:=NULL][, discNewLag7:=NULL][, new.reviews:=NULL]
```
